In-silico molecular enrichment and clearance of the human intracranial space

### 2025-01-23 paper/main.tex
A paragraph for the Discussion

>>>>

In conclusion, our findings transfer insights from experimental
studies and theoretical analysis to the in-silico human setting,
reconcile seemingly conflicting observations in particular relating to
directionality of perivascular flow, and integrate different physical
mechanisms across across spatial and temporal scales. The complete
simulation pipeline is openly available, including interactive
visualization of simulation results for all model
variations~\cite{ZENODO}. Looking ahead, this platform establishes a
foundation for in-silico studies of molecular movement within the
human brain environment, such as tailored predictions of intrathecal
chemotherapy delivery or personalized diagnostics of brain clearance
capacity.
